### 2018-04-07 Paper/ros.tex
...

>>>>

In this section, we focus our attention on constructing a surrogate that captures the dependence of
uncertainty in NEMD predictions for the bulk thermal conductivity ($\kappa$) on input variability
in the SW potential parameters. The surrogate is a powerful tool that greatly minimizes
the computational
effort required for forward propagation of the uncertainty from input parameters to the observable,
Sobol sensitivity analysis, and Bayesian calibration of the uncertain model parameters. Once again,
we use polynomial chaos (used to construct response surfaces for discrepancy in
Section~\ref{sec:response}) to construct the surrogate of the following functional form:

\be
\kappa  = \sum\limits_{\bm{s}\in\mathcal{A}} c_{\bm{s}}(T)\Psi_{\bm{s}}(\bm{\xi})
\ee

As discussed earlier in Section~\ref{sec:response}, several strategies are available to
estimate the PC coefficients, $c_{\bm{s}}$. However, since the polynomial basis functions
($\Psi_{\bm{s}}(\bm{\xi}$)) are
relatively high dimensional, we use a computationally efficient approach proposed by
Blatman and Sudret to construct a PCE with sparse basis($\mathcal{A}$) using the LAR
algorithm~\cite{Blatman:2011}. Furthermore, since the NEMD simulations are compute-intensive,
estimating the PC coefficients in the 7D parameter space would still require large amount of
computational resources. Hence, we explore the possibility of reducing the dimensionality of
the surrogate. For this purpose, we 
exploit our observations in Figure~\ref{fig:ub} where a signifcant
jump in $\hat{\mathcal{C}_i\mu_i}$ estimate is seen from $A$ to $B$ and therby construct the 
PC surrogate in a 5D parameter space by fixing $B$ and $p$ at their nominal values. In the above
equation, $\bm{\xi}:~\{\xi_1(A),\xi_2(q),\xi_3(\alpha),\xi_4(\lambda),\xi_5(\gamma)\}$ is a set
of five canonical random variables, $\xi_i$ distributed uniformly in the interval [-1,1]. 
For the five uniformly distributed SW parameters, the prior intervals are considered to be
$\pm~10\%$ of their respective nominal estimates except for $q$ in which case it is [0,0.1]. In
Figure~\ref{fig:loo}, we plot the leave-one-out cross-validation error 
($\epsilon_{\tiny{\mbox{LOO}}}$)~\cite{Blatman:2010} as defined
below in Eq.~\ref{eq:loo} against the number of model realizations used to construct the 5D
PC surrogate.

\be
\epsilon_{\tiny{\mbox{LOO}}} = \frac{\sum\limits_{i=1}^{N}\left(\mathcal{M}(\bm{x}^{(i)}) - 
\mathcal{M}^{PCE\setminus i}(\bm{x}^{(i)})\right)^{2}}{\sum\limits_{i=1}^{N}
\left(\mathcal{M}(\bm{x}^{(i)}) - \hat{\mu}_Y\right)^2}
\label{eq:loo}
\ee

\noindent where $N$ denotes the number of realizations, $\mathcal{M}(\bm{x}^{(i)})$ is the
model realization and $\mathcal{M}^{PCE\setminus i}(\bm{x}^{(i)})$ is the corresponding PCE estimate
at $\bm{x}^{(i)}$. Note that the PCE is constructed using all points except $\bm{x}^{(i)}$.
The quantity, $\hat{\mu}_Y$ = $\frac{1}{N}\sum\limits_{i=1}^{N}\mathcal{M}(\bm{x}^{(i)})$
is the sample mean of the realizations. 
It is found that in order for the PCE to converge to an accuracy of~$\mathcal{O}(10^{-2})$
with respect to $\epsilon_{\tiny{\mbox{LOO}}}$, we require approximately 160 NEMD runs. In the
following section, we focus on verifying the accuracy of the 5D PCE against the set of available
NEMD predictions in the original 7D parameter space.

### 2018-04-07 Paper/sense.tex
...

\noindent The NPT stage of the simulation was allowed to continue for a sufficiently long duration to ensure
that the system is relaxed to a steady value of the bar length as shown in Figure~\ref{fig:dgsm1}(b).

>>>>

\noindent The NPT stage of the simulation was allowed to continue for a sufficiently long duration to ensure
that the system is relaxed to a steady value of the bar length as shown in Figure~\ref{fig:dgsm1}(b).
The following algorithm provides the sequence of steps that were used to obtain approximate estimates of the
sensitivity measures for the SW potential parameters. Note that the algorithm has been adapted to the 
specific application in this work. A generalized methodology with a more detailed discussion and its application
to different class of problems will be presented in~\cite{Vohra:2018}.

\bigskip

\begin{breakablealgorithm}
  \caption{Estimating parameter ranks using DGSM.}
  \begin{algorithmic}[1]
    \Procedure{DGSM}{}
      \State Generate $n_1$ points in $\mathbb{R}^{d}$.\Comment{$d$: 
             Number of parameters i.e. 7 in this case}
      \State Perturb each point along the $d$ directions to obtain a set of $n_1(d+1)$ points.
      \State Compute $\mu_i$ using model evaluations at the $n_1(d+1)$ points in Eq.~\ref{eq:mu}
      \State Determine initial ranks, $\mathcal{R}^{old}$ based on $\hat{\mathcal{C}_i\mu_i}$ values.
      \State set $k$ = 1\Comment{Iteration counter}
      \Do
        \State Generate $n_k$ new points in $\mathbb{R}^{d}$.
        \State Perturb each point along the $d$ directions to obtain a set of $n_k(d+1)$ points.
        \State Compute and store model evaluations at the $n_k(d+1)$ points.
        \State Compute $\mu_i$ using prior model evaluations at $(d+1)(n_1 + \sum_j^k n_j)$ points.
        \State Determine new ranks, $\mathcal{R}^{new}$ based on updated $\hat{\mathcal{C}_i\mu_i}$ values.
        \State Compute $max\_pdev$ = max$\left(\frac{|\mu_{i,k} - 
               \mu_{i,k-1}|}{ \mu_{i,k-1}}\right)$.\Comment{$max\_pdev$:
               Maximum percentage deviation in $\mu_i$ between successive iterations.}
        \State set $k$ = $k$ + 1
      \doWhile{($\mathcal{R}^{\tiny{new}}$ $\neq$ $\mathcal{R}^{\tiny{old}}$ $\&$ 
               $max\_pdev$~$>~\tau$)\Comment{$\tau$:~Tolerance}}
    \EndProcedure
  \end{algorithmic}
\end{breakablealgorithm}

\bigskip

%\texttt{Algorithm}
%
%\begin{algorithm}[H]
%\SetAlgoLined
%%\nonl \scriptsize{\textsc{Part I: Parameter Screening}}
%%\nonl \textbf{\texttt{Algorithm}}\;
%\texttt{Generate $n_1$ points in $\mathbb{R}^{d}$}\;
%\texttt{Perturb each point along the $d$ directions to obtain a set of $n_1(d+1)$ points}
%\texttt{\color{blue} $\%$~$d$: Number of parameters in the SW potential i.e. 7}\;
%\texttt{Compute $\mu_i$ using model evaluations at the $n_1(d+1)$ points in Eq.~\ref{eq:mu}}\;
%\texttt{Determine initial ranks, $\mathcal{R}^{old}$ of the parameters based on $\hat{\mathcal{C}_i\mu_i}$ values}\;
%\texttt{set $k$ = 1}
%\texttt{\color{blue}$\%$~$k$:~Iteration counter}\;
%\Repeat{\texttt{($\mathcal{R}^{\tiny{new}}$ $\neq$ $\mathcal{R}^{\tiny{old}}$ $\&$ 
%$max\_pdev$~$>\tau$)~\color{blue}$\%$~$\tau$:~Tolerance}}{
%\texttt{Generate $n_k$ new points in $\mathbb{R}^{d}$}\;
%\texttt{Perturb each point along the $d$ directions to obtain a set of $n_k(d+1)$ points}\;
%\texttt{Compute and store model evaluations at the $n_k(d+1)$ points}\;
%\texttt{Compute $\mu_i$ using prior model evaluations at $(d+1)(n_1 + \sum_j^k n_j)$ points}\;
%\texttt{Determine new ranks, $\mathcal{R}^{new}$ based on updated $\hat{\mathcal{C}_i\mu_i}$ values}\;
%\texttt{Compute $max\_pdev$ = max($\frac{|\mu_{i,k} - \mu_{i,k-1}|}{ \mu_{i,k-1}}$)}
%\texttt{\color{blue}$\%$~$max\_pdev$: Maximum percentage deviation in $\mu_i$ between successive iterations.}\;
%\texttt{set $k$ = $k$ + 1}\;
%}
%\end{algorithm}

For the present application, we begin with $n_1$ = 10 samples in the 7D parameter space and add 5 points
at each iteration. Using a tolerance, $\tau$ = 0.05, the above algorithm took 4 iterations i.e. 25 points to 
provide approximate estimates for $\mu_i$. Since finite difference was used to estimate the derivates in
Eq.~\ref{eq:mu}, it required 25(7+1) i.e. 200 MD runs. It must be noted that although the computational effort
pertaining to the estimation of DGSM can be substantial, it is nevertheless several orders of magnitude smaller
than directly estimating the Sobol indices as mentioned earlier. 
In Figure~\ref{fig:ub}, we plot $\hat{\mathcal{C}_i\mu_i}$ as obtained for the SW parameters at the 
end of 4 iterations. It appears that $\gamma$ is significantly more important than other parameters, whereas NEMD
predictions are relatively less sensitive to $B$ and $p$. Large sensitivity towards 
$\gamma$ and $\alpha$ (cut-off radius) is in fact expected since  these two parameters impact the lattice
constant and hence the mean free path associated with the bulk thermal conductivity directly.

In the following section, we exploit these observations based on DGSM to construct a reduced order surrogate.
The surrogate enables forward propagation of uncertainty in the SW potential to the bulk thermal conductivity 
estimates, and the estimation of Sobol sensitivity indices with minimal computational effort.
